\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-04-15 investigation/docs/overview.tex
edits to the report doc

1. Determining the empirical p-values for each of the 501 interactions \\

@@

a. Identify which of the two snps in the original epistasis pair has the largest additive effect. \\

b. Treat the largest additive SNP as a fixed SNP and perform a genome-wide analysis using the 8df and 4df epistasis model. \\

c. This generates $\approx 500,000$ interaction p-values. Apply the same snp-pair filtering as used in the manuscript. Namely, LD ($r^2$ < 0.1), nclass $=$ 9, and minclass $>$ 5. Any SNP with +/- 5MB of original epistasis SNP pairs were also removed. \\

d.  Use the (filtered) interaction p-values to determine the empirical distribution of null p-values. \\

@@

\begin{figure}[H]
\centering
\includegraphics[width=3.5in]{lambda_107.png}
\caption*{Figure | Example of p-value distribution - ok}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=3.5in]{lambda_305.png}
\caption*{Figure | Example of p-value distribution - bad}
\end{figure}

>>>>

\textbf{1. GWAS based determination of the empirical p-values for each of the 501 interactions} \\

@@

a. The SNP with largest additive effect was identified for each pair of the 501 original epistasis SNPs. \\

b. The largest additive SNP was treated as a fixed SNP and a genome-wide analysis using the 8df and 4df epistasis model was performed. \\

c. This generated $\approx 500,000$ interaction p-values. The sample snp-pair filtering as used in the manuscript was applied. Namely, LD ($r^2$ < 0.1), nclass $=$ 9, and minclass $>$ 5. Any SNP with +/- 5MB of original epistasis SNP pairs were also removed. \\

d.  The filtered interaction p-values were used to determine the empirical distribution of null p-values. \\

e. Summary information such as median lambda were calculated from the filtered interaction p-values. \\

\textbf{2. Permutation based determination of the empirical p-values for each of the 501 interactions} \\

a. As before, the SNP with largest additive effect was identified for each pair of the 501 original epistasis SNPs. \\

b. Genotypes at the corresponding epistatitic ''co-SNP'' were randomly shuffled (no replacement) amongst individuals. \\

c. Interaction p-values and text statistics were calculated using the same methods. \\

d. For each pair (\emph{n}=501) this analysis was performed 10,000,000 times. \\

e. The same filtering was applied (although $r^2$ not required). \\

f. The empirical \emph{p}-value determined based on rank of observed \emph{F}-Statistic

@@
